Resumé title

### 2017-06-29 paper/coverletter.tex
APW edit

We submit the enclosed paper for consideration for a Nature Letter.
The paper lays out a simple and clear account for evidences in stellar
chemical abundances that massive rocky accretion happened in one of the two
stars that are comoving in space, and possibly also in the other one albeit in
smaller amount. Figure~2 demonstrates this key result where we compare
the abundance difference between the two stars with the change
expected from accretion of bulk Earth by a sun-like star.
We think the result is one of the most convincing examples that shows a
catastrophic ending possible to planets around sun-like stars, and thus will be
interesting to scientists in other disciplines as well as those in astronomy or
exoplanet field.

The document has been formatted with \LaTeX\ article class.
The summary is 286 words long, and the main text has $\approx 1424$ words,
29 references,
and two single-panel figures and one table, which should fit the page limit
of a Nature Letter.
We also include six extended data figure that will help interested readers
get the full context, as well as supplementary material discussing several
aspects of the main text in more detail.

>>>>

The enclosed paper presents clear evidence of massive accretion of rocky,
planetary material in the differential stellar chemical abundances of one star
in a comoving pair of sun-like stars. The other star in the pair also appears
to have accreted rocky material albeit in smaller amount. Figure~2 demonstrates
this key result: we show the abundance differences between the two stars
along with the change expected from accretion of bulk Earth material by a
sun-like star. We think that this result is the most convincing example of a
catastrophic end to planetary systems around sun-like stars, and thus will be
interesting to scientists in other disciplines as well as those in astronomy or
the exoplanets sub-field. We therefore submit the enclosed paper for
consideration for a Nature Letter.

The document has been formatted with the \LaTeX\ article class.
The summary is 286 words long, and the main text has $\approx 1424$ words,
29 references,
and two single-panel figures and one table, which should fit the page limit
of a Nature Letter.
We also include six extended data figures that will help interested readers
get the full context, as well as supplementary material discussing several
aspects of the main text in more detail.
